Associations between Chlorophyll *a* and various Microcystin-LR Health Advisory

### 2015-09-29 manuscript/manuscript.Rmd
added conf. matrix for mcstyn and chla

#Agreement Tables
child_conmat<-table(chla=nla_dat$CHLA>=mc_chla[1],mcsyt=nla_dat$MCYST_TL_UGL>=0.3)
who_drink_conmat<-table(nla_dat$CHLA>=mc_chla[2],nla_dat$MCYST_TL_UGL>=1)
adult_conmat<-table(nla_dat$CHLA>=mc_chla[3],nla_dat$MCYST_TL_UGL>=1.6)
who_rec_conmat<-table(nla_dat$CHLA>=mc_chla[4],nla_dat$MCYST_TL_UGL>=2)
#Want to minimize false negatives.  Ratio or FN/FP+TP+TN

>>>>

#Agreement Tables
child_conmat<-conmat_to_df(table(chla=nla_dat$CHLA>=mc_chla[1],
                                 mcsyt=nla_dat$MCYST_TL_UGL>=0.3))
who_drink_conmat<-conmat_to_df(table(nla_dat$CHLA>=mc_chla[2],
                        nla_dat$MCYST_TL_UGL>=1))
adult_conmat<-conmat_to_df(table(nla_dat$CHLA>=mc_chla[3],
                    nla_dat$MCYST_TL_UGL>=1.6))
who_rec_conmat<-conmat_to_df(table(nla_dat$CHLA>=mc_chla[4],
                      nla_dat$MCYST_TL_UGL>=2))
total_accuracy<-NULL
total_accuracy$epa_child<-round((child_conmat[1,1]+child_conmat[2,2])/
  sum(child_conmat),2)
total_accuracy$who_drink<-round((who_drink_conmat[1,1]+who_drink_conmat[2,2])/
  sum(who_drink_conmat),2)
total_accuracy$epa_adult<-round((adult_conmat[1,1]+adult_conmat[2,2])/
  sum(adult_conmat),2)
total_accuracy$who_rec<-round((who_rec_conmat[1,1]+who_rec_conmat[2,2])/
  sum(who_rec_conmat),2)

fn_percent<-NULL
fn_percent$epa_child<-round((child_conmat[1,2])/
  sum(child_conmat),2)
fn_percent$who_drink<-round((who_drink_conmat[1,2])/
  sum(who_drink_conmat),2)
fn_percent$epa_adult<-round((adult_conmat[1,2])/
  sum(adult_conmat),2)
fn_percent$who_rec<-round((who_rec_conmat[1,2])/
  sum(who_rec_conmat),2)

#Want to minimize false negatives.  Ratio of FN/FP+TP+TN
